An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-07-27 poly-embed-journal/poly-embed-journal.tex
Small comments in meeting prep

%\raf{Let's use $\H^*$ for the minimum one, here and below; $\H$ for another one}
%\raf{Similarly $\V^*$ for the minimum one, below; $\V$ for another one}
\begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
  Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, and for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
  Moreover, $\{H^+\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
\end{theorem}
\begin{proof}
  \jessie{TODO} \url{https://arxiv.org/abs/0805.0292} Prop 4.5?
\end{proof}
\jessie{Need to find a good reference.  Cite a result for polytopes and transform the polyhedra into a polytope. Could state the result for class of polyhedra containing $G$.
  Add two facets and now it's a polytope.
}

@@

\begin{claim}\label{claim:vface-subset-some-vstar-face}
  For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
  \jessie{Want to move this to the projections subsection, but technically we want this for the infinite version of $\V$.} 
\end{claim}
\begin{proof}
  $\{F_{v^*}\}_{v^* \in \V^*}$ is exactly the set of facets of $G$ on $\reals_+^d$ by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
  Any $k$-face is contained in a facet by Claim~\ref{claim:faces-contained-in-facets}.

  If it as a subset of a vertical facet, we would have $F_v = H_v \cap G \subseteq H_y \cap G$ for some $y \in \Y$.
  Expanding, this is $\{(x,g(x)) \mid \inprod{v}{x} = g(x)\} \subseteq \{(x,g(x)) \mid x_y = 0 \}$.
  While this can happen, it must be on the boundary of $\reals_+^d$, and must be at the intersection of $H_y$ and some other $H_{v^*}$ for $v^* \in \V^*$.

@@

\begin{corollary}\label{cor:f-matches-g-on-simplex}
  For all concave $f : \reals^\Y_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f) = \simplex$, there is a polyhedral concave function $g : \reals^\Y_+ \to \reals_+$ with $\dom(g) = \reals^\Y_+$ so that $f(p) = g(p)$ for all $p \in \simplex$.
\end{corollary}
Given the function $f$, we consider $g$ to be such its extension and $L$ such that $\risk L_+ = g$ so that we may use the tools in Phases 1 and 2 draw conclusions about the property $\Gamma$.

>>>>

%\raf{Let's use $\H^*$ for the minimum one, here and below; $\H$ for another one}
%\raf{Similarly $\V^*$ for the minimum one, below; $\V$ for another one}
\begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
  Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, and for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
  Moreover, $\{H\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
\end{theorem}
\begin{proof}
	Since $P$ is $d$-dimensional in $\reals^d$, it therefore has nonempty interior.

  \jessie{TODO} \url{https://arxiv.org/abs/0805.0292} Prop 4.5?
\end{proof}

\jessie{Need to find a good reference.  Cite a result for polytopes and transform the polyhedra into a polytope. Could state the result for class of polyhedra containing $G$.
  Add two facets and now it's a polytope.
}

@@

\begin{claim}\label{claim:vface-subset-some-vstar-face}
  For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
  \jessie{Want to move this to the projections subsection, but technically we want this for the infinite version of $\V$.} 
\end{claim}
\begin{proof}
  $\{F_{v^*}\}_{v^* \in \V^*}$ is exactly the set of facets of $G$ on $\reals_+^d$ by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
  Any $k$-face is contained in a facet by Claim~\ref{claim:faces-contained-in-facets}.
  Since $\H = \cap (\H_{\V^*} \cup \H_\Y)$, we are done if $F_v$ is contained in a face of $\H_{\V^*}$ and need to consider the case where $F_v \in \H_\Y$.

  If $F_v$ is a subset of a vertical facet, we would have $F_v = H_v \cap G \subseteq H_y \cap G$ for some $y \in \Y$.
  Expanding, this is $\{(x,g(x)) \mid \inprod{v}{x} = g(x)\} \subseteq \{(x,g(x)) \mid x_y = 0 \}$.
  While this can happen, it must be on the boundary of $\reals_+^d$, and must be at the intersection of $H_y$ and some other $H_{v^*}$ for $v^* \in \V^*$, since $g$ is continuous on $\reals^\Y_{+}$, and determined by $\V^*$ on $\reals^\Y_{++}$.

@@

\begin{corollary}\label{cor:f-matches-g-on-simplex}
  For all concave $f : \reals^\Y_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f) = \simplex$, there is a polyhedral concave function $g : \reals^\Y_+ \to \reals_+$ with $\dom(g) = \reals^\Y_+$ so that $f(p) = g(p)$ for all $p \in \simplex$.
\end{corollary}
Given the function $f$, we consider $g$ to be its extension and $L$ such that $\risk L_+ = g$ so that we may use the tools in Phases 1 and 2 draw conclusions about the property $\Gamma$.
